Screening harmonies

### 2020-06-04 choosing_harmonies_Normal.Rmd
choosing harmonies pdf update

## Theoretical evidence

@Menendez1997-in and @Grosse2002-ex provide studies of the statistical properties of the Jensen-Shannon divergences and suggest that the theoretical asymptotic distribution of Jensen-Shannon divergence converges to a Chi-squared distribution. Let $p^{(1)} \equiv (p_1^{(1)}, p_2^{(1)}, \dots, p_k^{(1)})$ and $p^{(2)} \equiv (p_1^{(2)}, p_1^{(2)}, \dots, p_k^{(2)})$ denote two probability distributions, where $k$ is the number of components of the probability vector p. Then 2N(ln2)D is known to converge to {$\chi^2$} distribution with degrees of freedom = (k - 1) and

$D[p^{(1)}, p^{(2)}] = H((p^{(1)} + p^{(2)})/2)  - H(p^{(1)}) - H(p^{(2)})$, $H_{(p)} = \sum_{i = 1}^{k} p_ilog_2p_i$ and N is the total number of events.

## Empirical evidence

However, since we are dealing with small finite samples, a more appropriate approach would be to look at the distribution of the samples through histogram, density plots or using QQ-plot to see how well the empirical quantiles match the theoretical quantiles. The QQ plots of four harmony pairs are plotted below. It could be seen that Chi-square distribution serves as a pretty good fit to the data (specially in the extreme right tail).

```{r}
library(tsibbledata)
library(ggplot2)
library(tsibble)
library(lvplot)
library(dplyr)
library(gravitas)
library(purrr)
library(magrittr)
sm <- smart_meter10 %>%
filter(customer_id %in% c(10017936))
.data = sm
gran1 = "wknd_wday"
gran2 = "hour_day"
response  = "general_supply_kwh"
```

### Distribution fitting of distances for the harmony pair (weekend/weekday, hour-of-day)

```{r}
.data %>% qqplot_distance(gran1 = "wknd_wday", gran2 = "hour_day", response = "general_supply_kwh")
```

### Distribution fitting of distances for the harmony pair (day-of-week, hour-of-day)

```{r}
.data %>% qqplot_distance(gran1 = "day_week", gran2 = "hour_day", response = "general_supply_kwh")
```

### Distribution fitting of distances for the harmony pair (hour-of-day, week-of-month)

```{r}
.data %>% qqplot_distance(gran1 = "hour_day", gran2 = "week_month", response = "general_supply_kwh")
```

### Distribution fitting of distances for the harmony pair (day-of-month, day-of-week)

```{r}
.data %>% qqplot_distance(gran1 = "day_month", gran2 = "day_week", response = "general_supply_kwh")
```

# Estimating parameters

Currently, MME is used. But MASS::fitdistr() and package fitdistrplus also provide methods to estimate parameters through MLE. WIP.

@@

Threholds could be chosen for distances (chi-squared) or maximum distance (Gumbel distribution).

Critical values of the Chi-squared statistic could be obtained for appropriate degrees of freedom.

Chi-squared statistic: And test values less than critical value would imply that the distances are not significantly different from zero , implying distributions are similar. If distributions are similar most times, then the plot is not interesting. Hence, all pairs for which most of the pairwise distances are significantly different from zero would only be included in the harmony rank table.

Gumbel statistic: The test decides if the sample of maximum distance is from Gumbel or not. If it is from Gumbel, the value of the test statistic should be ideally zero. And we want to take all pairs for which the statistic is significantly different from zero. So we choose test values greater than the Gumbel critical value at 5% significance.

@@

### Maximum distance between levels of x-axis variable and median across levels of facet variable

```{r}
library(readr)
smart_weibull <- read_rds("data/reverse_smart_weibull.rds")  %>% mutate(rank_weibull = row_number())

smart_gamma <- read_rds("data/reverse_smart_gamma.rds")  %>% mutate(rank_gamma = row_number())

smart_normal <- read_rds("data/reverse_smart_normal.rds") %>% mutate(rank_normal = row_number())

smart_chi <-read_rds("data/reverse_smart_chisq.rds") %>% mutate(rank_chi = row_number())
smart_general <- read_rds("data/reverse_smart_general.rds") %>% mutate(rank_general = row_number())

data_unite <- smart_chi %>% 
  left_join(smart_weibull, by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
   rename("chisq" = "mean_max_variation.x", "weibull" = "mean_max_variation.y") %>% 
    left_join(smart_gamma,  by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>%  
  rename("gamma" = "mean_max_variation") %>% 
  left_join(smart_normal,  by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
  rename("normal" = "mean_max_variation") %>% 
   left_join(smart_general,  by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
  rename("general" = "mean_max_variation") 
```

```{r}
data_unite %>% 
  select(-c(normal, gamma, weibull, general, chisq)) %>%
  dplyr::rename("normal"  = "rank_normal",
         "gamma"  = "rank_gamma",
         "weibull"  = "rank_weibull",
         "general"  = "rank_general",
         "chi"  = "rank_chi",
         "f_L" = "facet_levels",
         "x_L" = "x_levels") %>% 
  knitr::kable(format = "latex")

  threshold <- read_rds("data/smart_harmony_threshold.rds") %>% 
               mutate(thresval = "select") %>% 
    select(facet_variable, x_variable, thresval)

data_unite %>% 
  select(-c(normal, gamma, weibull, general, chisq)) %>%
  left_join(threshold, 
            by = c("facet_variable", "x_variable"))%>%
  select(-facet_levels, -x_levels) %>% 
    knitr::kable(format = "latex")

# data_unite %>%
#   select(-c(rank_normal, rank_gamma, rank_weibull, rank_general, rank_chi)) %>%
#   filter()
#   knitr::kable()
```

### Maximum distance between levels of facet variable and median across levels of x-axis variable

```{r}
library(readr)
smart_weibull <- read_rds("data/smart_harmony_wb.rds")  %>% mutate(rank_weibull = row_number())

smart_gamma <- read_rds("data/smart_gamma.rds")  %>% mutate(rank_gamma = row_number())

smart_normal <- read_rds("data/smart_harmony_norm.rds") %>% mutate(rank_normal = row_number())

smart_chi <-read_rds("data/smart_harmony_chisq.rds") %>% mutate(rank_chi = row_number())
smart_general <- read_rds("data/smart_general.rds") %>% mutate(rank_general = row_number())

data_unite <- smart_chi %>% 
  left_join(smart_weibull, by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
   rename("chisq" = "mean_max_variation.x", "weibull" = "mean_max_variation.y") %>% 
    left_join(smart_gamma,  by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>%  
  rename("gamma" = "mean_max_variation") %>% 
  left_join(smart_normal,  by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
  rename("normal" = "mean_max_variation") %>% 
   left_join(smart_general,  by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
  rename("general" = "mean_max_variation") 
```

```{r}
data_unite %>% 
  select(-c(normal, gamma, weibull, general, chisq)) %>% 
  dplyr::rename("normal"  = "rank_normal",
         "gamma"  = "rank_gamma",
         "weibull"  = "rank_weibull",
         "general"  = "rank_general",
         "chi"  = "rank_chi") %>% 
  knitr::kable(format = "latex")

# data_unite %>%
#   select(-c(rank_normal, rank_gamma, rank_weibull, rank_general, rank_chi)) %>% 
#   knitr::kable()
```

@@

```{r}
prob_plot(.data,  gran1 = "day_week", gran2 = "day_month", plot_type = "boxplot")

prob_plot(.data,  gran1 = "wknd_wday", gran2 = "day_month", plot_type = "boxplot")

prob_plot(.data,  gran1 = "wknd_wday", gran2 = "hour_day", plot_type = "boxplot")

@@

harmonies_cric <- cricket_data %>% harmony(lgran = "over", ugran = "match", filter_in = c("lag_field", "over"), hierarchy_tbl = hierarchy_model)

### Distribution fitting of distances for the harmony pair (lag_field, over)

```{r}
cricket_data  %>% qqplot_distance(gran1 = "lag_field", gran2 = "over", response = "runs_per_over", hierarchy_tbl = hierarchy_model)
```

```{r}
cric_weibull <- read_rds("data/cric_weibull.rds") %>% mutate(rank_weibull = row_number())

cric_gamma <-read_rds("data/cric_gamma.rds") %>% mutate(rank_gamma = row_number())

cric_normal <-read_rds("data/cric_normal.rds")%>% mutate(rank_normal = row_number())

cric_general <- read_rds("data/cric_general.rds")%>% mutate(rank_general = row_number())

cric_chisq <- read_rds("data/cric_chisq.rds")%>% mutate(rank_chisq = row_number())

data_unite <- cric_chisq %>% 
  left_join(cric_weibull, by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
   rename("chisq" = "mean_max_variation.x", "weibull" = "mean_max_variation.y") %>% 
    left_join(cric_gamma,  by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>%  
  rename("gamma" = "mean_max_variation") %>% 
  left_join(cric_normal,  by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
  rename("normal" = "mean_max_variation") %>% 
   left_join(cric_general,  by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
  rename("general" = "mean_max_variation") 
```

```{r}
data_unite %>% 
  select(-c(normal, gamma, weibull, general, chisq)) %>%
  dplyr::rename("normal"  = "rank_normal",
         "gamma"  = "rank_gamma",
         "weibull"  = "rank_weibull",
         "general"  = "rank_general",
         "chi"  = "rank_chisq") %>% 
  knitr::kable(format = "latex")

# data_unite %>%
#   select(-c(rank_normal, rank_gamma, rank_weibull, rank_general, rank_chi)) %>% 
#   knitr::kable()
```

### Maximum distance between levels of facet variable and median across levels of x-axis variable

```{r}
cric_weibull <- read_rds("data/ smart_cric_weibull.rds") %>% mutate(rank_weibull = row_number())

cric_gamma <-read_rds("data/ smart_cric_gamma.rds") %>% mutate(rank_gamma = row_number())

cric_normal <-read_rds("data/ smart_cric_normal.rds")%>% mutate(rank_normal = row_number())

cric_general <- read_rds("data/ smart_cric_general.rds")%>% mutate(rank_general = row_number())

cric_chisq <- read_rds("data/smart_cric_chisq.rds")%>% mutate(rank_chisq = row_number())

data_unite <- cric_chisq %>% 
  left_join(cric_weibull, by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
   rename("chisq" = "mean_max_variation.x", "weibull" = "mean_max_variation.y") %>% 
    left_join(cric_gamma,  by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>%  
  rename("gamma" = "mean_max_variation") %>% 
  left_join(cric_normal,  by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
  rename("normal" = "mean_max_variation") %>% 
   left_join(cric_general,  by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
  rename("general" = "mean_max_variation") 
```

```{r}
data_unite %>% 
  select(-c(normal, gamma, weibull, general, chisq)) %>%
  dplyr::rename("normal"  = "rank_normal",
         "gamma"  = "rank_gamma",
         "weibull"  = "rank_weibull",
         "general"  = "rank_general",
         "chi"  = "rank_chisq") %>% 
  knitr::kable(format = "latex")

# data_unite %>%
#   select(-c(rank_normal, rank_gamma, rank_weibull, rank_general, rank_chi)) %>% 
#   knitr::kable()
```

>>>>

@@

| facets/x-axis     	| A_1  	| A_2  	| A_3  	| .. 	| .. 	| A_K  	|
|-----	|------	|------	|------	|----	|----	|------	|
| B_1 	| p_11 	| p_12 	| p_13 	| .. 	| .. 	| p_1K 	|
| B_2 	|      	|      	|      	|    	|    	|      	|
| B_3 	|      	|      	|      	|    	|    	|      	|
| ..  	|      	|      	|      	|    	|    	|      	|
| ..  	|      	|      	|      	|    	|    	|      	|
| B_L 	| p_L1 	| p_L2 	| p_L3 	| .. 	| .. 	| p_LK 	|

$H_{01}: p_{11} = p_{21} = \ldots = p_{L1}$  
$H_{02}: p_{12} = p_{22} = \ldots = p_{L2}$  
\vdots
$H_{0K}: p_{1K} = p_{2K} = \ldots = p_{LK}$

$m$ = $L \choose 2$ (unordered)  
$m$ = $L-1$ (ordered)

|  facets/distances	| A_1  	| A_2  	| A_3  	| .. 	| .. 	| A_K  	|
|------------------	|------	|------	|------	|----	|----	|------	|
| d_1              	| d_11 	| d_12 	| d_13 	| .. 	| .. 	| d_1K 	|
| d_2              	|      	|      	|      	|    	|    	|      	|
| d_3              	|      	|      	|      	|    	|    	|      	|
| ..               	|      	|      	|      	|    	|    	|      	|
| ..               	|      	|      	|      	|    	|    	|      	|
| d_m              	| d_m1 	| d_m2 	| d_m3 	| .. 	| .. 	| d_mL 	|

$H_{01}: d_{11} = d_{21} = \ldots = d_{m1} = 0$  
$H_{02}: d_{12} = d_{22} = \ldots = d_{L2} = 0$  
\vdots
$H_{0m}: d_{1m} = d_{2m} = \ldots = d_{Lm} = 0$

 - can do ANOVA at this stage
 - interpretation of results (if interaction of levels significant when testing if means of distributions of distances are equal to zero )

| facets/max-dist 	| A_1       	| A_2       | .. 	| .. 	| A_K       	|
|-----------------	|-----------	|-----------	|-----------	|----	|----	|-----------	|
| max-dist        	| max(d_11, .., dm1) 	| max(d_12, ...d_m2) 	| .. 	| .. 	| max(d_1K,...d_mK) 	|

$H_{01}: max(d_{11}, .., d_{m1}) = 0$  
$H_{02}: max(d_{12}, ...d_{m2})  = 0$  
\vdots
$H_{0K}: max(d_{1K},...d_{mK}) = 0$

 -  normalised maximum distribution follows standardised Gumbel distribution
 -  multiple hypothesis testing problem where p-values needs to be adjusted with Fisher's combination test (preferred) or Bonferroni's correction
 - What is the test statistic for multiple hypothesis problem?

@@

normal: standard normal ordered distances  
normal_nonstd: non-standard normal ordered distances  
normal_un: standard normal unordered distances  
normal_nonstd_un: non-standard normal unordered   distances

```{r}
library(readr)
smart_normal <- read_rds("data/ smart_harmony_normal.rds")  %>% mutate(rank_normal = row_number())

smart_normal_nonstd <- read_rds("data/smart_harmony_nonstd.rds") %>% mutate(rank_normal_nonstnd = row_number())

smart_normal_un <- read_rds("data/smart_harmony_normal_unordered.rds")  %>% mutate(rank_normal_un = row_number())

smart_normal_nonstd_un <- read_rds("data/smart_harmony_nonstd_unordered.rds") %>% mutate(rank_normal_nonstnd_un = row_number())

smart_normal %>% 
  left_join(smart_normal_nonstd, by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
   rename("normal" = "mean_max_variation.x", "normal_nonstd" = "mean_max_variation.y") %>%

  left_join(smart_normal_un, by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
  rename("normal_un" = "mean_max_variation") %>%

  left_join(smart_normal_nonstd_un, by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
  rename("normal_nonstd_un" = "mean_max_variation")%>% select(-c(normal, normal_nonstd, normal_un, normal_nonstd_un))%>%
  dplyr::rename("normal"  = "rank_normal",
         "normal_nonstd"  = "rank_normal_nonstnd",
         "normal_un"  = "rank_normal_un",
         "normal_nonstd_un"  = "rank_normal_nonstnd_un")%>%   knitr::kable(format = "latex")
```

<!-- # unordered -->

<!-- ```{r} -->
<!-- library(readr) -->
<!-- smart_normal <- read_rds("data/smart_harmony_normal_unordered.rds")  %>% mutate(rank_normal = row_number()) -->

<!-- smart_normal_nonstd <- read_rds("data/smart_harmony_nonstd_unordered.rds") %>% mutate(rank_normal_nonstnd = row_number()) -->

<!-- smart_normal %>%  -->
<!--   left_join(smart_normal_nonstd, by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>%  -->
<!--    rename("normal" = "mean_max_variation.x", "normal_nonstd" = "mean_max_variation.y") %>%  -->
<!--   select(-c(normal, normal_nonstd))%>% -->
<!--   dplyr::rename("normal_unordered"  = "rank_normal", -->
<!--          "normal_nonstd_unordered"  = "rank_normal_nonstnd")%>%   knitr::kable(format = "latex") -->
<!-- ``` -->

@@

```{r}
smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>% prob_plot( gran1 = "day_week", gran2 = "day_month", plot_type = "boxplot")

smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>% prob_plot(gran1 = "wknd_wday", gran2 = "day_month", plot_type = "boxplot")

smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>% 
  prob_plot(gran1 = "wknd_wday", gran2 = "hour_day", plot_type = "boxplot")

@@

harmonies_cric <- cricket_data %>% harmony(lgran = "over", ugran = "match", filter_in = c("lag_field", "over"), hierarchy_tbl = hierarchy_model)
```
